\newpage
\begin{center}
\thispagestyle{empty}
\vspace*{2\baselineskip}
\LARGE{\textbf{ABSTRACT}}\\[0.5cm]
\end{center}
\thispagestyle{empty}
\doublespacing
\begin{normalsize}
Books play the most important role in our life! Books help us to give the knowledge. We can 
read a book while relaxing, leisure time and they provide good source of knowledge. Books 
are our teachers, friends and guides and philosopher also. They provide enriching experience 
and thoughts. So we called "BOOKS ARE HUMAN'S BEST FRIEND."
The app brings the power of books at your fingertips. Its combines the world of Google books 
store into one single place with a very simple, easy to understand interface.
No expert knowledge and learning curve involved.
This system is an app developed on the basis of Android. Android Studio  are used as tools to develop this. When you read a good book, you can see others and see yourself, and you can get a lot of insights every time. Reading is a very popular thing to do. No matter how busy a job is, people will spend a certain amount of time buying books and reading books. The app design page is beautiful, friendly user interface, high user experience, on the online bookstore app, buyers and bookstore managers can achieve their own needs. Book purchasers can quickly buy their favorite books. Bookstore administrators can deal with orders formed after book buyers' books in the first time and update books in bookstores in time. The development of such app is of great significance for economic development, and much more convenient for consumers to use.
\\[1cm]
\end{normalsize}