\newpage
%\vspace*{1\baselineskip}
\begin{center}
\thispagestyle{empty}
\LARGE{\textbf{ACKNOWLEDGEMENTS}}\\[1cm]
\end{center}
\vspace{0.05cm}
\doublespacing


We present with immense pleasure this work titled \textbf{”Book Store App”}. An endeavour over a long period can be successful with the advice and support of
many well wishers.


We take this opportunity to express our gratitude and appreciation
to all of them.
The satisfaction and euphoria that accompany the successful completion of any
task would be incomplete without mentioning the people who made it possible. So,
with gratitude we acknowledge all those whose guidance and encouragement made to
successfully complete this project.


We would like to express sincere thanks to our Principal \textbf{Dr. Pradeep S}, Malnad
College of Engineering for his encouragement made to successfully completion of the
project work.
We wish to express our gratitude to \textbf{Dr.Geetha Kiran A}, Professor and Head,
Department of Computer Science \& Engineering for providing a good working environment and for her constant
support and encouragement.


It gives great pleasure in placing on record a deep sense of gratitude to our guide
\textbf{Mr. Shashidhara H V},Associate Professor, Department of Computer Science \& Engineering for his daily evaluation of the work and for providing us constant encouragement with his unflinching support and valuable guidance throughout this project.

We would also like to thank all the staff of Computer Science and Engineering
department who have directly or indirectly helped us in the completion of the project
work.
At last we would hereby acknowledge and thank our parents who have been a
source of inspiration and also instrumental in the successful completion of the project
work. \\
\large{\hspace*{4.5in} Chirag.K.Deshbhandari}\\
\large{\hspace*{4.5in} Vinay Chandra}


