\chapter{Brief explanation regarding Book Store App}\label{code}
\begin{normalsize}
People today are more inclined towards online purchase, from booking tickets for flights to purchase groceries online, our lives are majorly dependent on mobile apps. When it comes to buying books, there is no exception.The online bookstore apps give authors and bookstore vendors a platform to sell or rent books to the people who love to read in exchange for some specific amount of money. Through the online bookstore marketplace, a community of readers can easily browse their favorite books, authors, genres, etc., by making an account on the app.
In the past year, the market share of online bookstores has grown exponentially. Bookstore mobile apps have generated higher revenue during this time, and it all happens because of the outbreak of the pandemic. The covid-19 situation made people ponder on their reading habits and to start with the book which they always wanted to read.
According to a survey, the global online book services market size was estimated at 17.7 billion USD in 2019, and the numbers are expected to grow at a CAGR of 5.8% from 2020 to 2027. 
By the year 2027, the global online book service market is expected to earn 27.8 billion USD as revenue.It is also believed that around 12000 people go online book shopping in a day.To leverage the huge numbers, we can plan a book store mobile app that not only can give our business great exposure but also connect our brand with potential customers easily.Amazon has revolutionized the way of selling and purchasing books. Today, people from any part of the world can read a book of their choice, published and printed in different parts of the country. The community of book readers is large, and one must have a suitable online book store mobile application to cater to the diverse book requirements of readers.In the current situation of the pandemic, the physical book stores which were flooded with people are now empty. Amidst this, having a suitable mobile application will be a perfect choice.

\\[1cm]
\end{normalsize}